---
title: "Radicalization Lab"
subtitle: "Code sheet 2: Initial linear mixed effect model analyses"
author: "Arda Ergin"
output:
  rmdformats::downcute:
    downcute_theme: "chaos"
---

**CAUTION: This code is (kinda) deprecated!** I am keeping it here for archive purposes. Since this code, I have am incorporating ILR transformation and trying out other analyses other than mixed effect models. Essentially, mixed effect modelling (and, hence, this code) can still work for ILR-transformed variables, so can come back to it.


# Setup
IMPORTANT FOR THE USER OF THIS SCRIPT: you have to load the R package "**RadLab**". This is necessary for the code to work properly. See [the GitHub repository](https://github.com/ardaergin/RadLab) for further information.           

The code below loads the RadLab package, you need to download the "devtools" package first, you can do so with install.packages("devtools").
```{r, message=FALSE, warning=FALSE}
# First install the package with: 

devtools::install_github("ardaergin/RadLab")
library(RadLab)
library(haven)
library(dplyr)
library(stats)
library(lme4)
library(lmerTest)
library(optimx)
library(readxl)
```

```{r Imports}
load('data_working/d_study1.Rdata')
load('data_working/d_study2.Rdata')
load('data_working/d_study3.Rdata')
load('data_working/d_study4.Rdata')
load('data_working/d_study5.Rdata')
load('data_working/d_study6.Rdata')
```


# -------------


# Study 1 (2019-2020)

## Model comparisons
```{r}
study1_models <- d_study1 %>% RadLab::run_models()
```

```{r, results='asis'}
RadLab::get_model_comparisons(study1_models)
```

## Best model full results
```{r}
RadLab::get_model_results(models_list = study1_models)
```

## Best model summary
```{r, results='asis'}
RadLab::get_pretty_summaries(study1_models)
```



# Study 2 (2020-2021)

## Model comparisons
```{r}
study2_models <- d_study2 %>% RadLab::run_models()
```

```{r, results='asis'}
RadLab::get_model_comparisons(study2_models)
```

## Best model full results
```{r}
RadLab::get_model_results(models_list = study2_models)
```

## Best model summary
```{r, results='asis'}
RadLab::get_pretty_summaries(study2_models)
```



# Study 3 (2020-2021)

## Model comparisons
```{r}
study3_models <- d_study3 %>% RadLab::run_models()
```

```{r, results='asis'}
RadLab::get_model_comparisons(study3_models)
```

## Best model full results
```{r}
RadLab::get_model_results(models_list = study3_models)
```

## Best model summary
```{r, results='asis'}
RadLab::get_pretty_summaries(study3_models)
```



# Study 4 (2020-2021)

## Model comparisons
```{r}
study4_models <- d_study4 %>% RadLab::run_models()
```

```{r, results='asis'}
RadLab::get_model_comparisons(study4_models)
```

## Best model full results
```{r}
RadLab::get_model_results(models_list = study4_models)
```

## Best model summary
```{r, results='asis'}
RadLab::get_pretty_summaries(study4_models)
```



# Study 5 (2021-2022)

## Model comparisons
```{r}
study5_models <- d_study5 %>% RadLab::run_models()
```

```{r, results='asis'}
RadLab::get_model_comparisons(study5_models)
```

## Best model full results
```{r}
RadLab::get_model_results(models_list = study5_models)
```

## Best model summary
```{r, results='asis'}
RadLab::get_pretty_summaries(study5_models)
```



# Study 6 (2022-2023)

## Model comparisons
```{r}
study6_models <- d_study6 %>% RadLab::run_models()
```

```{r, results='asis'}
RadLab::get_model_comparisons(study6_models)
```

## Best model full results
```{r}
RadLab::get_model_results(models_list = study6_models)
```

## Best model summary
```{r, results='asis'}
RadLab::get_pretty_summaries(study6_models)
```


