---
title: "aaa"
output: html_document
date: "2023-09-11"
---


# Setup
IMPORTANT FOR THE USER OF THIS SCRIPT: you have to load the R package "**RadLab**". This is necessary for the code to work properly. See [the GitHub repository](https://github.com/ardaergin/RadLab) for further information.           

The code below loads the RadLab package, you need to download the "devtools" package first, you can do so with install.packages("devtools").
```{r, message=FALSE, warning=FALSE}
# First install the package with: 
devtools::install_github("ardaergin/RadLab")
library(RadLab)
library(dplyr)
library(haven)
library(stats)
library(lme4)
library(lmerTest)
library(optimx)

```



# -------------



### Modelling


```{r}
# Load necessary libraries
library(compositions)
library(zCompositions)
library(lme4)
library(dplyr)
library(ggplot2)

# Prepare your data
df <- d_study1_long %>%
  mutate(
    inaction_prop = ina / 100,
    normative_prop = na / 100,
    nonnormative_prop = nna / 100,
    extreme_nonnormative_prop = enna / 100
  )

# Create a matrix of the compositional data
comp_matrix <- as.matrix(
  df[, c('inaction_prop',
         'normative_prop',
         'nonnormative_prop',
         'extreme_nonnormative_prop')]
)

# Replace zeros using the multiplicative replacement method
comp_matrix_nozeros <- cmultRepl(
  comp_matrix, method = "CZM", output = "prop", label = 0
)

# Use zPatterns to see the pattern of zeros
zPatterns(comp_matrix, label = 0)

# Create acomp object with labels
comp_data <- acomp(comp_matrix_nozeros)

# Perform ilr transformation
ilr_data <- ilr(comp_data)

# Convert ilr_data to a data frame and name the columns
ilr_df <- as.data.frame(ilr_data)
colnames(ilr_df) <- c('ilr1', 'ilr2', 'ilr3')

# Combine with your original data
df_ilr <- cbind(df, ilr_df)

# Exclude rows with NA in 'gender_f' before modeling
df_ilr <- df_ilr %>%
  filter(!is.na(gender_f))

# Ensure 'gender_f' is a factor with correct levels
df_ilr$gender_f <- factor(df_ilr$gender_f, levels = c("Female", "Male"))

# Fit the models without NAs
model_ilr1 <- lmer(
  ilr1 ~ time +
    excluded + injustice + personal + violence +
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr
)

model_ilr2 <- lmer(
  ilr2 ~ time +
    excluded + injustice + personal + violence +
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr
)

model_ilr3 <- lmer(
  ilr3 ~ time +
    excluded + injustice + personal + violence +
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr
)

# Predict ilr values using fixed effects only
pred_ilr1 <- predict(model_ilr1, newdata = df_ilr, re.form = NA)
pred_ilr2 <- predict(model_ilr2, newdata = df_ilr, re.form = NA)
pred_ilr3 <- predict(model_ilr3, newdata = df_ilr, re.form = NA)

# Back-transform to compositional proportions
pred_ilr_full <- data.frame(ilr1 = pred_ilr1, ilr2 = pred_ilr2, ilr3 = pred_ilr3)
pred_comp <- ilrInv(pred_ilr_full)

# Assign unique component names to predicted proportions
colnames(pred_comp) <- c('pred_inaction_prop', 'pred_normative_prop', 'pred_nonnormative_prop', 'pred_extreme_nonnormative_prop')

# Add predicted proportions to df_ilr
df_ilr <- cbind(df_ilr, pred_comp)
```




### Modelling New



```{r}
# Model ilr1 as a function of time and extremity, with random intercepts and slopes for each participant
model_ilr1 <- lmer(
  ilr1 ~ time + 
    excluded + injustice + personal + violence + 
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr,
  na.action = na.exclude
)

model_ilr2 <- lmer(
  ilr2 ~ time + 
    excluded + injustice + personal + violence + 
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr,
  na.action = na.exclude
)

model_ilr3 <- lmer(
  ilr3 ~ time + 
    excluded + injustice + personal + violence + 
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr,
  na.action = na.exclude
)
```


```{r}
# List of predictor variables
predictor_vars <- c("time", "excluded", "injustice", "personal", "violence", "gender_f", "age")

# Check if all predictor variables are present in df_ilr
all(predictor_vars %in% names(df_ilr))

# Check for NA values in predictor variables
sapply(df_ilr[, predictor_vars], function(x) sum(is.na(x)))

df_ilr_complete <- df_ilr %>%
  filter(complete.cases(.[, predictor_vars]))


# Predict ilr1 values using fixed effects only
pred_ilr1 <- predict(model_ilr1, newdata = df_ilr, re.form = NA)

# Similarly for ilr2 and ilr3
pred_ilr2 <- predict(model_ilr2, newdata = df_ilr, re.form = NA)
pred_ilr3 <- predict(model_ilr3, newdata = df_ilr, re.form = NA)

# 3. Back-transform to compositional proportions
pred_ilr_full <- data.frame(ilr1 = pred_ilr1, ilr2 = pred_ilr2, ilr3 = pred_ilr3)
pred_comp <- ilrInv(pred_ilr_full)
colnames(pred_comp) <- c('inaction_prop', 'normative_prop', 'nonnormative_prop', 'extreme_nonnormative_prop')

# 4. Add predictions to df_ilr
df_ilr <- cbind(df_ilr, pred_comp)

# 5. Visualize results
ggplot(df_ilr, aes(x = time, y = inaction_prop, group = ID)) +
  geom_line(alpha = 0.3) +
  stat_summary(aes(group = 1), fun = mean, geom = "line", color = "blue", size = 1.5) +
  labs(title = "Predicted Inaction Proportion Over Time",
       x = "Time",
       y = "Predicted Inaction Proportion")

```




```{r}
# Predict ilr values
pred_ilr <- predict(model_ilr1, newdata = df_ilr)

# Combine ilr predictions with other ilr components (if needed)
pred_ilr_full <- cbind(pred_ilr, df_ilr[, c('ilr2', 'ilr3')])

# Back-transform to the compositional space
pred_comp <- ilrInv(pred_ilr_full)

```


```{r}
# Example plot of predicted inaction proportion over time
library(ggplot2)

df_ilr$pred_inaction <- pred_comp[, 'inaction_prop']

ggplot(df_ilr, aes(x = time, y = pred_inaction, group = ID)) +
  geom_line(alpha = 0.3) +
  stat_smooth(aes(group = 1), method = "loess", se = FALSE, color = "blue") +
  labs(title = "Predicted Inaction Proportion Over Time",
       x = "Time",
       y = "Predicted Inaction Proportion")

```








### Modelling
```{r Study 1 - Modelling}
study1_models <- d_study1_long %>% RadLab::run_models()

RadLab::get_model_results(models_list = study1_models)
```

```{r, results='asis'}
cat(sjPlot::tab_model(
        study1_models[["na"]][["M_LM"]],
        study1_models[["na"]][["M_LMER_simple"]],
        study1_models[["na"]][["M_LMER_complex"]])$knitr)
```

```{r, results='asis'}
RadLab::get_pretty_summaries(
  study1_models)

RadLab::get_model_comparisons(
  study1_models)
```


### Compositional
```{r}
library(compositions)
library(tidyverse)
library(robCompositions)
library(lme4)

# SETUP
# DV
Ym = compositions::acomp(d_study1_long[,7:10])
# IVs
###### QUESTİON: TAKİNG TİME AS FACTOR???
Xm0_f = factor(d_study1_long$time, ordered = TRUE)
Xm0 = d_study1_long$time
Xm1 = d_study1_long$excluded
Xm2 = d_study1_long$injustice
Xm3 = d_study1_long$personal
Xm4 = d_study1_long$violence
MIXEDO = d_study1_long$ID


# Linear Model

# 'Time' as Continuous
model_n <- lm(formula = compositions::ilr(Ym) ~ log(Xm0))
summary(model_n)
anova(model_n)

# 'Time' as factor
model_f <- lm(formula = compositions::ilr(Ym) ~ Xm0_f)
summary(model_f)
anova(model_f)
```




```{r}
d_study1_long[,7:10]
Utest1 <- zCompositions::lrEM(d_study1_long[,7:10], label = 0, dl = rep(1,4))
```


```{r}
attach(df3)
Utest <- data.frame(sed_min, lightlife_min, mod_min, vig_min)
colnames(Utest) <- c("sed", "light", "mod", "vig") 
Utest1 <- zCompositions::lrEM(Utest, label = 0, dl = rep(1,4))
detach(df3)

z1 <- pivotCoord(Utest1, pivotvar = 1)        
z2 <- pivotCoord(Utest1, pivotvar = 2)
z3 <- pivotCoord(Utest1, pivotvar = 3)
z4 <- pivotCoord(Utest1, pivotvar = 4)

ILR.data <- data.frame(z1, z2, z3, z4)
nhanes2 <- data.frame(Utest1, ILR.data, df3$seqn)
colnames(nhanes2) [17]  <- "seqn" 

demo_c <- nhanes("DEMO_C")

attach(demo_c)
demo_2003 <- data.frame(SEQN, WTMEC2YR, RIDAGEYR)
detach(demo_c)
colnames(demo_2003) [1]  <- "seqn" 

nhanes4 <- merge(nhanes2, demo_2003, by = "seqn")
colnames(nhanes4) [(19)] <- "age" 

```


```{r}
# SETUP
# DV
Ym = compositions::acomp(d_study1_long[,7:10])
# IVs


###### QUESTİON: TAKİNG TİME AS FACTOR???
Xm0_f = factor(d_study1_long$time, ordered = TRUE)
Xm0 = d_study1_long$time
Xm1 = d_study1_long$excluded
Xm2 = d_study1_long$injustice
Xm3 = d_study1_long$personal
Xm4 = d_study1_long$violence
MIXEDO = d_study1_long$ID

# Linear Model

# 'Time' as Continuous
model_n <- lm(formula = compositions::ilr(Ym) ~ log(Xm0))
summary(model_n)
anova(model_n)

# 'Time' as factor
model_f <- lm(formula = compositions::ilr(Ym) ~ Xm0_f)
summary(model_f)
anova(model_f)

mixed_model <- lme4::lmer(compositions::ilr(Ym) ~ Xm0 + (1|MIXEDO))

mixed_model <- lmer(Ym_ilr ~ time + (1|ID), data = d_study1_long)

Ym <- compositions::acomp(d_study1_long[, 7:10])

# Applying ilr transformation
Ym_ilr <- compositions::ilr(Ym)

# Building the model
mixed_model <- lmer(Ym_ilr ~ time + (1|ID), data = d_study1_long)
simplified_model <- lmer(Ym_ilr[,1] ~ time + (1|ID), data = d_study1_long)

```

```{r}
Ym_ilr_df <- as.data.frame(Ym_ilr)
names(Ym_ilr_df) <- c("Comp1", "Comp2", "Comp3")
d_study1_long_combined <- cbind(d_study1_long, Ym_ilr_df)

brm_model <- brm(cbind(Comp1, Comp2, Comp3) ~ time + (1|ID),
                 data = d_study1_long_combined,
                 family = gaussian(),
                 chains = 4, iter = 2000)
summary(brm_model)

```


```{r}
library(MCMCglmm)

# Assuming Ym_ilr is already a part of d_study1_long
d_study1_long$Comp1 <- Ym_ilr[, 1]
d_study1_long$Comp2 <- Ym_ilr[, 2]
d_study1_long$Comp3 <- Ym_ilr[, 3]

# Define priors
# The V matrix should be a 3x3 matrix because there are 3 response variables
prior <- list(R = list(V = diag(3), nu = 1),  # nu > 0
              G = list(G1 = list(V = diag(3), nu = 1)))  # Adjusted priors

# Fit the model
model <- MCMCglmm(cbind(Comp1, Comp2, Comp3) ~ time,
                  random = ~idv(ID),
                  family = c("gaussian", "gaussian", "gaussian"),
                  prior = prior,
                  data = d_study1_long,
                  verbose = FALSE)

summary(model)

library(MCMCglmm)

# Define 3x3 diagonal matrices for priors
prior_R <- list(V = diag(3), nu = 3)  # Residual errors prior
prior_G <- list(G1 = list(V = diag(3), nu = 3))  # Random effects prior

# Fit the model
model <- MCMCglmm(cbind(Comp1, Comp2, Comp3) ~ time,
                  random = ~us(1|ID),  # Random effects
                  family = c("gaussian", "gaussian", "gaussian"),
                  prior = list(R = prior_R, G = prior_G),
                  data = d_study1_long,
                  verbose = FALSE)

summary(model)

```



```{r}
library("brms")
brm_model <- brm(cbind(Ym_ilr[, 1], Ym_ilr[, 2], Ym_ilr[, 3]) ~ time + (1|ID),
                 data = d_study1_long,
                 family = gaussian(),
                 chains = 4, iter = 2000)
summary(brm_model)

```



# Study 2 (2020-2021)



## Import
```{r Study 2 - Import}
d_study2_0 <- haven::read_spss(
  'data/2_meike.sav')
```



## Exclusion
```{r Study 2 - Exclusion}
####### Informed Consent #######
# First excluding "Informed Consent is NA"
# Then based on "Informed Consent is 0"
d_study2_1 <- d_study2_0 %>% 
  dplyr::filter(!is.na(Consent)) %>% 
  dplyr::filter(Consent == 1)

## Number of participants excluded based on Informed Consent
nrow(d_study2_0) - nrow(d_study2_1)


####### Progress #######
d_study2_2 <- d_study2_1 %>% 
  dplyr::filter(Progress > 95)

## Number of participants excluded based on Progress
nrow(d_study2_1) - nrow(d_study2_2)
```



## Cleaning
Specifically for this data, in between measures for the vignettes, Meike has a "exclusion" and "fair" measure. They make it difficult to take the relevant columns. Hence, I am first going to delete those columns from the dataset.
```{r Study 2 - Cleaning}
####### Columns  #######
# Only Selecting the Relevant Columns
d_study2_3 <- d_study2_2 %>% 
  subset(select = -grep("exclusion_fair|eclusion_fair", names(.))) %>% 
  subset(select = -c(40:45)) %>% 
  subset(select = c(20:79,
                    3, # Condition
                    80, # Gender (gender)
                    81, # Age (age)
                    103, # liberal_conservative_rec
                    104 # left_right_rec
                    ))


# Assigning ID to the participants:
d_study2_3$ID <- 
  nrow(d_study1) + # Number of Participants in Hartog
  1:nrow(d_study2_3)

# Assigning experiment number to all participants in this dataset
d_study2_3$Experiment <- 2

# Converting the Columns to Numeric 
d_study2 <- RadLab::convert_df(d_study2_3)
```



## Means Plot
```{r Study 2 - Means Plot}
d_study2[, 1:60] %>% RadLab::graph_means(
  name_data = o_study2,
  n_vignettes = 15)
```



## Data Analysis
### Structuring Data
```{r Study2 - Structuring}
d_study2_long_0 <- d_study2 %>% RadLab::wide_to_long(
  name_data = o_study2,
  n_vignettes = 15)
```



### Factorizing
```{r Study 2 - Factorizing}
##### Factorizing #####


# Condition
d_study2_long_0 <- d_study2_long_0 %>%
  dplyr::mutate(
    condition_f = factor(
      haven::labelled_spss(Condition),
      levels = 1:3,
      labels = paste("Condition", 1:3)))


# Gender
d_study2_long_0 <- d_study2_long_0 %>%
  dplyr::mutate(
    gender_f = factor(
      haven::labelled_spss(gender),
      levels = 1:2,
      labels = c("Female", "Male")))


# Taking out the already converted variables
d_study2_long <- d_study2_long_0 %>% subset(select = -c(Condition, gender))
```



### Comp Modelling


```{r}
# Load necessary libraries
library(compositions)
library(zCompositions)
library(lme4)
library(dplyr)
library(ggplot2)

# Prepare your data
df <- d_study2_long %>%
  mutate(
    inaction_prop = ina / 100,
    normative_prop = na / 100,
    nonnormative_prop = nna / 100,
    extreme_nonnormative_prop = enna / 100
  )

# Create a matrix of the compositional data
comp_matrix <- as.matrix(
  df[, c('inaction_prop',
         'normative_prop',
         'nonnormative_prop',
         'extreme_nonnormative_prop')]
)

# Replace zeros using the multiplicative replacement method
comp_matrix_nozeros <- cmultRepl(
  comp_matrix, method = "CZM", output = "prop", label = 0
)

# Use zPatterns to see the pattern of zeros
zPatterns(comp_matrix, label = 0)

# Create acomp object with labels
comp_data <- acomp(comp_matrix_nozeros)

# Perform ilr transformation
ilr_data <- ilr(comp_data)

# Convert ilr_data to a data frame and name the columns
ilr_df <- as.data.frame(ilr_data)
colnames(ilr_df) <- c('ilr1', 'ilr2', 'ilr3')

# Combine with your original data
df_ilr <- cbind(df, ilr_df)

# Exclude rows with NA in 'gender_f' before modeling
df_ilr <- df_ilr %>%
  filter(!is.na(gender_f))

# Ensure 'gender_f' is a factor with correct levels
df_ilr$gender_f <- factor(df_ilr$gender_f, levels = c("Female", "Male"))

# Fit the models without NAs
model_ilr1 <- lmer(
  ilr1 ~ time +
    excluded + injustice + personal + violence +
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr
)

model_ilr2 <- lmer(
  ilr2 ~ time +
    excluded + injustice + personal + violence +
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr
)

model_ilr3 <- lmer(
  ilr3 ~ time +
    excluded + injustice + personal + violence +
    gender_f + (1 + time | ID),
  control = lmerControl(optimizer = "Nelder_Mead"),
  data = df_ilr
)

# Predict ilr values using fixed effects only
pred_ilr1 <- predict(model_ilr1, newdata = df_ilr, re.form = NA)
pred_ilr2 <- predict(model_ilr2, newdata = df_ilr, re.form = NA)
pred_ilr3 <- predict(model_ilr3, newdata = df_ilr, re.form = NA)

# Back-transform to compositional proportions
pred_ilr_full <- data.frame(ilr1 = pred_ilr1, ilr2 = pred_ilr2, ilr3 = pred_ilr3)
pred_comp <- ilrInv(pred_ilr_full)

# Assign unique component names to predicted proportions
colnames(pred_comp) <- c('pred_inaction_prop', 'pred_normative_prop', 'pred_nonnormative_prop', 'pred_extreme_nonnormative_prop')

# Add predicted proportions to df_ilr
df_ilr <- cbind(df_ilr, pred_comp)

# Visualize results
ggplot(df_ilr, aes(x = time, y = pred_inaction_prop, group = ID)) +
  geom_line(alpha = 0.3) +
  stat_summary(aes(group = 1), fun = mean, geom = "line", color = "blue", linewidth = 1.5) +
  labs(title = "Predicted Inaction Proportion Over Time",
       x = "Time",
       y = "Predicted Inaction Proportion")

```

```{r}
install.packages("MCMCglmm")
library(MCMCglmm)
prior <- list(R = list(V = diag(3), nu = 0.002),
              G = list(G1 = list(V = diag(3), nu = 0.002)))
mcmc_model <- MCMCglmm(cbind(ilr1, ilr2, ilr3) ~ trait:(time + excluded + injustice + personal + violence + gender_f) - 1,
                       random = ~ us(trait):ID,
                       rcov = ~ us(trait):units,
                       family = rep("gaussian", 3),
                       data = df_ilr,
                       prior = prior,
                       verbose = FALSE)

summary(mcmc_model)
```

```{r}
residuals_df <- data.frame(
  res_ilr1 = resid(model_ilr1),
  res_ilr2 = resid(model_ilr2),
  res_ilr3 = resid(model_ilr3)
)
cor(residuals_df)
```



```{r}
install.packages("brms")
library(brms)
formula <- bf(ilr1 ~ time + excluded + injustice + personal + violence + gender_f + (1 + time | ID)) +
           bf(ilr2 ~ time + excluded + injustice + personal + violence + gender_f + (1 + time | ID)) +
           bf(ilr3 ~ time + excluded + injustice + personal + violence + gender_f + (1 + time | ID))
brms_model <- brm(formula, data = df_ilr, chains = 4, cores = 4)

```


```{r}
fixed_effects <- summary(mcmc_model)$solutions

newdata <- df_ilr

# Create design matrix for fixed effects
# Extract the fixed effects coefficients
beta <- fixed_effects[, "post.mean"]
names(beta) <- rownames(fixed_effects)

# For each trait (ilr coordinate), compute the linear predictor
# Prepare the design matrix for each trait
predictors <- c("time", "excluded", "injustice", "personal", "violence", "gender_f")

# Initialize a data frame to store predicted ilr coordinates
predicted_ilr <- data.frame(ID = newdata$ID, time = newdata$time)

for (trait in c("ilr1", "ilr2", "ilr3")) {
  # Construct the variable names in beta
  beta_names <- paste0("trait", trait, ":", predictors)
  # Subset beta coefficients for the trait
  beta_trait <- beta[beta_names]
  # Ensure the order matches the predictors
  beta_trait <- beta_trait[beta_names]

  # Create the design matrix for the predictors
  X <- model.matrix(~ time + excluded + injustice + personal + violence + gender_f, data = newdata)
  # Remove the intercept (since we used '-1' in the model formula)
  X <- X[, -1]

  # Compute the linear predictor for the trait
  eta <- as.vector(X %*% beta_trait)

  # Store the predicted ilr values
  predicted_ilr[[trait]] <- eta
}

```


```{r}
library(compositions)

# Convert predicted ilr coordinates to a matrix
ilr_pred_matrix <- as.matrix(predicted_ilr[, c("ilr1", "ilr2", "ilr3")])

# Back-transform to compositions
pred_comp <- ilrInv(ilr_pred_matrix)

# Assign component names
colnames(pred_comp) <- c("ina", "na", "nna", "enna")

# Combine with the predicted ilr and predictors
pred_results <- cbind(predicted_ilr, pred_comp)

```

```{r}
library(tidyr)

# Reshape compositions to long format
pred_long <- pred_results %>%
  select(ID, time, ina, na, nna, enna) %>%
  pivot_longer(
    cols = c("Inaction", "Normative", "Nonnormative", "Extreme.Nonnormative"),
    names_to = "Action",
    values_to = "Proportion"
  )

```



# Modeling try 2









