---
title: "Radicalization Lab"
subtitle: "Code sheet 3: Data Preparation"
author: "Arda Ergin"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    downcute_theme: "chaos"
---

# Setup
```{r, message=FALSE, warning=FALSE}
devtools::load_all(here::here())
library(here)
library(dplyr)
library(tidyr)
library(ggplot2)
library(compositions)
library(zCompositions)
library(knitr)
```

```{r}
df <- readRDS(
  here::here("data", "experiments_merged.rds")
)
cat("Loaded data with", nrow(df), "observations.")
```



# Exploratory Data Analysis

## Check: NAs
```{r}
# Numerical Check for Missing Values
cat("=== Missing Values (NAs) ===\n")
cols_to_check <- c("ina", "na", "nna", "enna")

cat("Count:\n")
colSums(is.na(df[cols_to_check]))

cat("Proportions:\n")
colMeans(is.na(df[cols_to_check]))

# Verification: The columns must not have NAs for CoDA
if(any(is.na(df[cols_to_check]))) {
  warning("STOP: You have NAs in your compositional columns. You must impute or remove them before proceeding.")
} else {
  cat("\nCheck passed: No NAs found in compositional columns.\n")
}
```


## Check: Zeros
```{r}
# Numerical Check
cat("=== Zeros ===\n")
cat("Count:\n")
cols_to_check <- c("ina", "na", "nna", "enna")
colSums(df[cols_to_check] == 0, na.rm = TRUE)
cat("Proportions:\n")
colMeans(df[cols_to_check] == 0, na.rm = TRUE)
```

```{r}
# Visual Check
comp_cols <- df[, c("ina", "na", "nna", "enna")]

# label = 0 tells it what value to treat as zero
zCompositions::zPatterns(comp_cols, label = 0)
```

**Interpretation of the pattern table above**:
- There are $15$ possible scenarios present on missingness. Since we have $4$ variables, there are $2^4 = 16$ theoretically possible patterns. Since we are seeing $15$, it means 1 pattern, likely the "all zeros" pattern, is missing, which makes sense because participants must allocate points somewhere.
- In the plot/table, a *colored cell* (or "-" in the text output) means **a Non-Zero value** (they allocated points), and a *blue cell* (or "+" in text) means **a Zero** (they ignored that option). E.g., ("0", "no 0", "no 0", "no 0") means "ina is zero, but others are non-zero".
- The horizontal bars on the right show how many participants fall into that specific "Row" (Pattern). The longer the bar, the more common that behavior is.
- The vertical bars at the very top of the grid show the total count of zeros for each column (ina, na, etc.) independently.


## Check: Pairwise zeros & equality
In the ILR transformation, $0$ represents both double-zero as well as both of them having the same value (e.g., a participants assign 20 to NNA and 20 to ENNA). The model can't tell the difference between someone who gave 50 points to both (very radical) and someone who gave 0 to both (not radical at all). So it is good to check these cases.

```{r}
# 1. Get all unique pairwise combinations
vars <- c("ina", "na", "nna", "enna")
pairs <- combn(vars, 2, simplify = FALSE)

# 2. Iterate through pairs and calculate stats
pairwise_stats <- lapply(pairs, function(p) {
  v1 <- p[1]
  v2 <- p[2]
  
  df %>%
    summarise(
      Comparison = paste0(v1, " vs ", v2),
      Total_N = n(),
      Both_Zero_N = sum(get(v1) == 0 & get(v2) == 0),
      Both_Zero_Pct = (Both_Zero_N / Total_N) * 100,
      # Only check equality for cases where they AREN'T both zero
      Equal_NonZero_N = sum(get(v1) == get(v2) & get(v1) > 0),
      Equal_NonZero_Pct = (Equal_NonZero_N / Total_N) * 100
    )
}) %>%
  bind_rows()

# 3. Display the Table
kable(pairwise_stats, 
      digits = 2, 
      col.names = c("Pairwise Comparison", "Total N", "Both Zero (N)", "Both Zero (%)", "Equal Non-Zero (N)", "Equal Non-Zero (%)"),
      caption = "Table: Pairwise comparisons for 1) Both Zero 2) Both Non-Zero but Equal")
```


## Plot: Distributions
```{r, fig.width=8, fig.height=12}
RadLab::plot_stacked_distributions(
  data     = df,
  cols     = c("ina", "na", "nna", "enna"),
  labels   = c("Inaction", "Normative Action", "Non-Normative Action", "Extreme Non-Normative Action"),
  colors   = c("#475569", "#1e40af", "#d97706", "#991b1b"),
  title    = "Distribution of Allocated Points",
  xlab     = "Points Allocated (0-100)",
  x_breaks = seq(0, 100, 10),
  x_limits = c(0, 100)
)
```


## Plot: Distributions without 0 and 100
```{r, fig.width=8, fig.height=12}
RadLab::plot_stacked_distributions(
  data     = df,
  cols     = c("ina", "na", "nna", "enna"),
  labels   = c("Inaction", "Normative Action", "Non-Normative Action", "Extreme Non-Normative Action"),
  colors   = c("#475569", "#1e40af", "#d97706", "#991b1b"),
  title    = "Distribution of Allocated Points",
  subtitle = "Excluding 0 and 100", # <---
  xlab     = "Points Allocated (0-100)",
  x_breaks = seq(0, 100, 10),
  x_limits = c(0, 100),
  exclude_values = c(0, 100) # <---
)
```


# CoDA Transformations

## CZM + ILR

### Apply Zero Replacement
```{r}
comp_counts <- as.matrix(
  df[, c("ina","na","nna","enna")]
)

comp_counts_nozeros <- zCompositions::cmultRepl(
  comp_counts,
  method = "CZM",
  output = "prop",
  label = 0,
  threshold = 0.5,
  frac = 0.65,
  z.delete = FALSE
)
```


### Define Basis Matrices
```{r}
# A:
## ILR_1: INA vs. (NA + NNA + ENNA)
## ILR_2: NA vs. (NNA + ENNA)
## ILR_2: NNA vs. ENNA
custom_basis_A <- matrix(c(
  -0.8660254,  0.0000000,  0.0000000,    # inaction
   0.2886751, -0.8164966,  0.0000000,    # normative
   0.2886751,  0.4082483, -0.7071068,    # non-normative
   0.2886751,  0.4082483,  0.7071068     # extreme non-normative
),
nrow = 4, ncol = 3, byrow = TRUE,
dimnames = list(
  c("ina","na","nna","enna"),
  c("b1","b2","b3")
  )
)

# A:
# ILR_1: ENNA vs (INA + NA + NNA)
# ILR_2: NNA vs (INA + NA)
# ILR_2: NA vs INA
custom_basis_B <- matrix(c(
  -0.2886751, -0.4082483, -0.7071068,  # inaction
  -0.2886751, -0.4082483,  0.7071068,  # normative
  -0.2886751,  0.8164966,  0.0000000,  # non-normative
   0.8660254,  0.0000000,  0.0000000   # extreme non-normative
), nrow = 4, ncol = 3, byrow = TRUE,
dimnames = list(
  c("ina","na","nna","enna"), 
  c("b1","b2","b3")
  )
)

custom_basis_matrices <- list(
  A = custom_basis_A, 
  B = custom_basis_B
)
```


### ILR Transformation
```{r}
# Create acomp object
acomp_obj <- compositions::acomp(comp_counts_nozeros)

# 4. Loop through bases matrices and append ILR coordinates
for (basis_name in names(custom_basis_matrices)) {
  # Perform ILR
  V <- custom_basis_matrices[[basis_name]]
  ilr_mat <- compositions::ilr(acomp_obj, V = V)
  ilr_df  <- as.data.frame(ilr_mat)
  
  # Rename columns (e.g., ilr_theory_1, ilr_theory_2...)
  colnames(ilr_df) <- paste0(
    "ilr_", basis_name, "_", 1:ncol(ilr_df)
  )
  
  # Bind to df
  df <- cbind(df, ilr_df)
  
  cat(paste("Calculated ILR coords for the basis matrix:", basis_name, "\n"))
}
```



### Check: NAs
```{r}
# Identify the new ILR columns we just created
ilr_cols <- grep("^ilr_", names(df), value = TRUE)

cat("=== Missing Values (NAs) in ILR Coordinates ===\n")

cat("Count:\n")
colSums(is.na(df[ilr_cols]))

cat("Proportions:\n")
colMeans(is.na(df[ilr_cols]))

# Verification
if(any(is.na(df[ilr_cols]))) {
  warning("STOP: You have NAs in your ILR coordinates. This usually happens if a row had all zeros even after CZM, or if the basis matrix is singular.")
} else {
  cat("\nCheck passed: No NAs found in ILR coordinates.\n")
}
```



### ILR visualizations
#### Plot: Aitchison Variation Matrix
```{r}
# Compute the variation matrix
var_mat <- compositions::variation(acomp_obj)

# Pretty‐print and heatmap
kable(round(var_mat, 3), caption = "Aitchison Variation Matrix")
stats::heatmap(var_mat, symm=TRUE, main="Aitchison Variation")
```

#### Plot: PCA & Biplot
```{r}
# Compute CLR (centered log‐ratio)
clr_df <- as.data.frame(clr(acomp_obj))

# PCA
p <- stats::prcomp(clr_df, scale.=FALSE)

# Biplot
stats::biplot(p, xlabs=rep(".", nrow(clr_df)), main="CLR‐PCA Biplot")
```

#### Plot: Distribution
```{r, fig.width=8, fig.height=12}
# Quick range check for ILR variables
ilr_range_check <- df %>%
  dplyr::select(starts_with("ilr_")) %>%
  summarise(across(everything(), list(min = min, max = max)))
print(ilr_range_check)
```

```{r, fig.width=8, fig.height=8}
for (basis_name in names(custom_basis_matrices)) {
  plot <- plot_stacked_distributions(
    data           = df,
    cols           = paste0("ilr_", basis_name, "_", 1:3),
    labels         = c("ILR 1", "ILR 2", "ILR 3"),
    colors         = c("#8e44ad", "#2c3e50", "#16a085"),
    title          = "Distribution of ILR Coordinates",
    subtitle       = paste("Basis Matrix:", basis_name),
    xlab           = "ILR Value (Log-Ratio)",
    x_breaks       = seq(-5, 5, 1),
    x_limits       = c(-5, 5),
    show_zero_line = TRUE,
    bins           = 100
  )
  print(plot)
}
```


## Hellinger
```{r}
df$ina_hellinger  <- sqrt(df$ina / 100)
df$na_hellinger   <- sqrt(df$na / 100)
df$nna_hellinger  <- sqrt(df$nna / 100)
df$enna_hellinger <- sqrt(df$enna / 100)

# Verify creation
head(df[, c("ina_hellinger", "na_hellinger", "nna_hellinger", "enna_hellinger")])
```

### Plot: Distributions
```{r, fig.width=8, fig.height=12}
plot_stacked_distributions(
  data     = df,
  cols     = c("ina_hellinger", "na_hellinger", "nna_hellinger", "enna_hellinger"),
  labels   = c("Inaction", "Normative Action", "Non-Normative Action", "Extreme Non-Normative Action"),
  colors   = c("#475569", "#1e40af", "#d97706", "#991b1b"),
  title    = "Distribution of Hellinger-Transformed Allocations",
  xlab     = "Hellinger Value (0-1)",
  x_breaks = seq(0, 1, 0.1),
  x_limits = c(0, 1)
)
```

### (!) Inversion
Inversion (Directionality alignment for lcmm::multlcmm)
- 1.0 = High Radicalization (e.g., Low inaction),
- 0.0 = Low Radicalization (e.g., High inaction),
```{r}
df$ina_hellinger_inv <- 1 - df$ina_hellinger
df$na_hellinger_inv  <- 1 - df$na_hellinger
```


## Checking everything
```{r}
# 1. Identify all transformed columns (ILR and Hellinger)
vars_to_verify <- grep("ilr_|hellinger", names(df), value = TRUE)

cat("=== Post-Transformation Validity Check ===\n")

# 2. Create the summary table
# We use vars_to_verify for both the rows and the data selection
validity_summary <- data.frame(
  Variable = vars_to_verify,
  NAs      = sapply(df[vars_to_verify], function(x) sum(is.na(x))),
  NaNs     = sapply(df[vars_to_verify], function(x) sum(is.nan(x))),
  Infs     = sapply(df[vars_to_verify], function(x) sum(is.infinite(x)))
)

# 3. Print the results
print(validity_summary)

# 4. Final Verdict
total_issues <- sum(validity_summary[, c("NAs", "NaNs", "Infs")])

if(total_issues > 0) {
  warning("STOP: Detected ", total_issues, " invalid values in transformed variables.")
} else {
  cat("\nCheck passed: All transformed variables are finite and complete.\n")
}
```





# Other variables

## Time

```{r}
df %>%
  group_by(experiment) %>%
  summarise(Tmax = max(time, na.rm=TRUE), .groups="drop") %>%
  arrange(Tmax)
```

```{r}
# Relative time (per experiment)
df <- df %>%
  group_by(experiment) %>%
  mutate(
    time_min_exp = min(time, na.rm = TRUE),
    time_max_exp = max(time, na.rm = TRUE),
    time_relative = ifelse(
      time_max_exp == time_min_exp,
      0,  # edge case: only 1 timepoint in an experiment
      (time - time_min_exp) / (time_max_exp - time_min_exp)
    )
  ) %>%
  ungroup() %>%
  dplyr::select(-time_min_exp, -time_max_exp)
hist(df$time_relative)
```


```{r}
# 1) Centered (units = "scenario steps")
time_mean <- mean(df$time, na.rm = TRUE)
df$time_c <- df$time - time_mean

# 2) Centered + scaled (units = SD of scenario steps)
time_sd <- sd(df$time, na.rm = TRUE)
df$time_z <- (df$time - time_mean) / time_sd

# 3) MinMax normalization
## This is apparently bad, but doing it here just to check out the correlation below
df$time_minmax <- df$time / max(df$time)
```


```{r}
# Checks
## Original
cat("cor(time, time^2) =", cor(df$time, df$time^2), "\n")

## MinMax
cat("cor(time_minmax, time_minmax^2) =", cor(df$time_minmax, df$time_minmax^2), "\n")

## Center / Centered + scaled
cat("cor(time_c, time_c^2) =", cor(df$time_c, df$time_c^2), "\n")
cat("cor(time_z, time_z^2) =", cor(df$time_z, df$time_z^2), "\n")

## Relative
cat("cor(time_relative, time) =", cor(df$time_relative, df$time), "\n")
cat("cor(time_relative, time_relative^2) =", cor(df$time_relative, df$time_relative^2), "\n")
cat("cor(time_relative, time_z) =", cor(df$time_relative, df$time_z), "\n")
cat("cor(time_relative, time_c) =", cor(df$time_relative, df$time_c), "\n")
```


## Ensure type
```{r}
df <- df %>%
  mutate(
    # Time
    time       = as.numeric(time),
    time_c     = as.numeric(time_c),
    time_z     = as.numeric(time_z),
    time_minmax= as.numeric(time_minmax),
    time_relative = as.numeric(time_relative),
    # Others
    ID         = as.integer(as.factor(ID)),
    experiment = as.factor(experiment)
  )
```

# Save
```{r}
saveRDS(df, file = here::here(
  "data", "experiments_processed.rds")
)
cat("Saved transformed data to data/experiments_analysis.rds")
```

